Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections

### 2022-11-14 elife_submission/manuscript.tex
Minor adjustments to submission

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections},
  pdfauthor={Johannes ElferichGiulia SchiroliDavid ScaddenNikolaus Grigorieff},
  pdflang={en-US},
  pdfkeywords={cryo-EM, visual protemics, ribosome},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\usepackage[margin=2cm]{geometry}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage{cleveref}
\usepackage{fontspec}
\setmainfont{texgyrepagella}[
  Extension = .otf,
  UprightFont = *-regular,
  BoldFont = *-bold,
  ItalicFont = *-italic,
  BoldItalicFont = *-bolditalic,
]
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{caption}
\captionsetup[figure]{font={stretch=1.2}}

%% pandoc-fignos: environment for tagged figures
\newenvironment{fignos:tagged-figure}[1][]{
    \let\oldthefigure\thefigure
    \let\oldtheHfigure\theHfigure
    \renewcommand{\thefigure}{#1}
    \renewcommand{\theHfigure}{#1}
  }{
    \let\thefigure\oldthefigure
    \let\theHfigure\oldtheHfigure
    \addtocounter{figure}{-1}
  }
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

A major goal of biological imaging is localization of biomolecules inside a cell. Fluorescence microscopy can localize biomolecules inside whole cells
and tissues, but its ability to count biomolecules and accuracy of the spatial
coordinates is limited by the wavelength of visible light. Cryo-electron
microscopy (cryo-EM) provides highly accurate position and orientation
information of biomolecules but is often confined to small fields of view inside
a cell, limiting biological context. In this study we use a new data-acquisition
scheme called ``Defocus-Corrected Large-Area cryo-EM'' (DeCo-LACE) to collect
high-resolution images of entire sections (100 -- 200 nm thick lamellae)
of neutrophil-like mouse cells, representing 1-2\% of the total cellular
volume. We use 2D template matching (2DTM) to determine localization and orientation of the large ribosomal subunit in these sections. These data provide ``maps'' of ribosomes across entire sections of mammalian cells. This high-throughput cryo-EM data collection approach together with 2DTM will advance visual proteomics and provide biological insight that cannot be obtained by other methods.

@@

We used the tile positions to calculate the positions of the detected
LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig. {[}\ref{fig:matching_fff}{]}A, Movie 1, Movie 2). Overlaying these positions of the lamellae montages reveals LSU
distribution throughout the FIB-milled slices of individual cells. Consistent with prior observations imaging selected views in yeast {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, organelles
like the nucleus and mitochondria only showed sporadic targets detected with low
SNRs, consistent with the estimated false-positive rate of one per tile. For
each detected target we also calculated the Z positions from the individual
estimated defocus and defocus offset for each tile. When viewed from the side,
the ribosome positions therefore show the slight tilts of the lamellae relative
to the microscope frame of reference (Fig. {[}\ref{fig:matching_euc}{]}B, Fig.
{[}\ref{fig:matching_fff}{]}B, Movie 1, Movie 2). Furthermore, the side views indicated that lamellae
were thinner at the leading edge. Indeed, when plotting the transmitted beam
intensities in individual tiles as a function of beam image-shift, we observed
substantially higher intensities at the leading edge (Fig. {[}\ref{fig:lamella_motion_thickness}{]}B), which in energy-filtered
TEM indicates a thinner sample {[}\protect\hyperlink{ref-17IP4Lhz1}{18}{]}. Even though we prepared the lamellae
with the ``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{19}{]}, this means that LSU densities across
the lamellae can be skewed by a change in thickness, and better sample
preparation methods are needed to generate more even samples.

@@

Close inspection of the LSU positions in the lamellae revealed several
interesting features. LSUs could be seen associating with membranes, in
patterns reminiscent of the rough endoplasmic reticulum (Fig.
{[}\ref{fig:matching_euc}{]}C, Fig. {[}\ref{fig:matching_fff}{]}C) or the outer nuclear
membrane (Fig. {[}\ref{fig:matching_euc}{]}D). We also observed LSUs forming
ring-like structures (Fig. {[}\ref{fig:matching_euc}{]}E), potentially indicating
circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{20}{]}. While ribosomes were for the most part excluded
from the numerous granules observed in the cytoplasm, in some cases we observed
clusters of LSUs in the inclusions of double-membraned granules
described earlier (Fig. {[}\ref{fig:matching_euc}{]}F, Fig. {[}\ref{fig:matching_fff}{]}D,E). It is, in principle, possible that these targets are situated above or
below the imaged granules, since the granule positions in z cannot be determined
using 2D projections. However, in the case of Fig. {[}\ref{fig:matching_fff}{]}E, the
detected LSUs span the whole lamella in the z direction (Fig. {[}\ref{fig:matching_fff}{]}F), while positions
above or below a granule would result in LSUs situated exlusively at the
top or bottom of the lamella. This is consistent with the earlier hypothesis that the inclusions are of
cytoplasmic origin.

@@

In this study we developed an approach to image entire cellular cross-section using cryo-EM at high enough resolution to allow for 2DTM detection of the LSU. The two main advantages compared to previous approaches are high throughput of imaging and biological context for detected molecules. The requirement to increase throughput in cryo-EM data collection of cellular samples has been recognized in the recent literature. Most approaches described so far are tailored towards tomography. Peck et al. {[}\protect\hyperlink{ref-1GPPSX111}{21}{]} and Yang et al. {[}\protect\hyperlink{ref-ujizcpVn}{22}{]} developed approaches to increase the FOV of tomogram data-collection by using a montaging technique. Peck et al.~used a similar ``condensed-beam'' approach as described here. However, the montages are substantially smaller in scope, covering carbon film holes of 2 µm diameter. Bouvette et al. {[}\protect\hyperlink{ref-1Gwx5ScUa}{23}{]} and Eisenstein et al. {[}\protect\hyperlink{ref-xvouNMBy}{24}{]} are using beam image-shift to collect tilt-series in multiple locations in parallel to increase throughput. However, none of these approaches provide the full coverage of a cellular cross-section that can be achieved using DeCo-LACE.

We observed granules containing a vesicle of putative cytosolic origin. We speculate that upon degranulation, the process in which granules fuse with the plasma membrane, these vesicles would be released into the extracelullar space. The main types of extracellular vesicles of this size are exosomes, up to 100 nm large vesicles derived from fusion of multivesicular bodies with the plasma membrane, and microvesicles, which are derived from direct budding of the plasma membrane {[}\protect\hyperlink{ref-kncnYGLD}{25}{]}. We suggest that granulocytes could release a third type of extracellular vesicle, granule-derived vesicles (GDV), into the extracellular space. 2DTM showed that a subset of GDVs can contain ribosomes (Fig. {[}\ref{fig:matching_euc}{]}F, Fig. {[}\ref{fig:matching_fff}{]}D,E). This could indicate that these vesicles are transporting translation-capable mRNAs, as has been described for exosomes {[}\protect\hyperlink{ref-agVdpX76}{26}{]}. Further studies will be necessary to confirm the existence of GDVs in granulocytes isolated from mammals and to understand their functional significance.

@@

We found that even though we used beam image-shift extensively (up to 7 um), we did not see substantially reduced 2DTM SNR values in tiles acquired at high beam image-shift compared to tiles acquired with low or no beam image-shift. This is in contrast to reports in single-particle analysis (SPA) {[}\protect\hyperlink{ref-44fG6kcy}{27}{]} where the induced beam tilt substantially reduced the resolution if it was not corrected during processing. It is possible that 2DTM is less sensitive to beam-tilt aberrations, since the template is free of any aberration and only the image is distorted, while in SPA the beam tilt will affect both the images and the reconstructed template.

Since we observed substantial variation in LSU density within and between lamellae, visual proteomics studies that use cryo-EM to establish changes in molecular organization within cells will require orders of magnitude more data than used in this study. One milestone would be to image enough data to represent one cellular volume, which for a small eukaryotic cells requires imaging approximately 100 lamellae. While data collection throughput on the TEM is fundamentally limited by the exposure time, this amount of data could be collected within 12 hours by improving the data acquisition scheme to perform all necessary calculations in parallel with actual exposure of the camera. Sample preparation using a FIB/SEM is also currently a bottleneck, but preparation of large lamellae with multiple cellular cross-sections using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{28}{]} might allow sufficient throughput. As stated in the results, at least for 2DTM computation will remain challenging and approximately 17,000 GPU hours would be required for a 100 lamellae dataset.

@@

@@

ER-HoxB8 cells were maintained in RPMI medium supplemented with 10\% FBS,
penicillin/streptomycin, SCF, and estrogen {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} at
37 °C and 5\% CO2. 120 h prior to grid preparation, cells were washed twice in PBS
and cultured in the same medium except without estrogen. Differentiation was
verified by staining with Hoechst-dye and inspection of nuclear morphology.
Cells were then counted and diluted to \(1\cdot10^6\) cells/ml. Grids (either 200
mesh copper grids, with a sillicone-oxide and 2 µm holes with a 2 µm spacing or
200 mesh gold grids with a thin gold film and 2 µm holes in 2 µm spacing) were
glow-discharged from both sides using a 15 mA for 45 s. 3.5 µl of cell suspension
was added to grids on the thin-film side and grids were blotted from the back
side using a GP2 cryoplunger (Leica, Wetzlar, Germany) for 8 s and rapidly plunged into liquid
ethane at -185 °C.

@@

A list of tile pairs \(i,j\) that overlap were assembled by selecting images where
\(|\mathbf{c}_i-\mathbf{c}_j| < D_{Beam}\). In order to calculate the precise offset between tiles \(i\) and \(j\), \(\mathbf{r}_{i,j}\), we calculated the cross-correlation between the two tiles, masked to the overlapping illuminated area using the scikit-image
package {[}\protect\hyperlink{ref-stvWEJeu}{34}{]} was used to calculate refined offsets . The coordinates \(\mathbf{c}_{i}\) were then refined by a least-square minimization against \(\mathbf{r}_{i,j}\):

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections},
  pdfauthor={Johannes ElferichGiulia SchiroliDavid ScaddenNikolaus Grigorieff},
  pdflang={en-US},
  pdfkeywords={cryo-EM, visual protemics, ribosome},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\usepackage[margin=2cm]{geometry}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage{cleveref}
\usepackage{fontspec}
\setmainfont{texgyrepagella}[
  Extension = .otf,
  UprightFont = *-regular,
  BoldFont = *-bold,
  ItalicFont = *-italic,
  BoldItalicFont = *-bolditalic,
]
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{caption}
\captionsetup[figure]{font={stretch=1.2}}

%% pandoc-fignos: environment for tagged figures
\newenvironment{fignos:tagged-figure}[1][]{
    \let\oldthefigure\thefigure
    \let\oldtheHfigure\theHfigure
    \renewcommand{\thefigure}{#1}
    \renewcommand{\theHfigure}{#1}
  }{
    \let\thefigure\oldthefigure
    \let\theHfigure\oldtheHfigure
    \addtocounter{figure}{-1}
  }

%% pandoc-tablenos: required package
\usepackage{caption}

%% pandoc-tablenos: environment to disable table caption prefixes
\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}

}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}

}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

A major goal of biological imaging is localization of biomolecules
inside a cell. Fluorescence microscopy can localize biomolecules inside
whole cells and tissues, but its ability to count biomolecules and
accuracy of the spatial coordinates is limited by the wavelength of
visible light. Cryo-electron microscopy (cryo-EM) provides highly
accurate position and orientation information of biomolecules but is
often confined to small fields of view inside a cell, limiting
biological context. In this study we use a new data-acquisition scheme
called ``Defocus-Corrected Large-Area cryo-EM'' (DeCo-LACE) to collect
high-resolution images of entire sections (100 -- 250 nm thick lamellae)
of neutrophil-like mouse cells, representing 1-2\% of the total cellular
volume. We use 2D template matching (2DTM) to determine localization and
orientation of the large ribosomal subunit in these sections. These data
provide ``maps'' of ribosomes across entire sections of mammalian cells.
This high-throughput cryo-EM data collection approach together with 2DTM
will advance visual proteomics and provide biological insight that
cannot be obtained by other methods.

@@

We used the tile positions to calculate the positions of the detected
LSUs in the lamellae (Fig. {[}\ref{fig:matching_euc}{]}A, Fig.
{[}\ref{fig:matching_fff}{]}A, Fig. {[}\ref{fig:matching_euc}{]}-video 1, Fig.
{[}\ref{fig:matching_fff}{]}-video 1). Overlaying these positions of
the lamellae montages reveals LSU distribution throughout the FIB-milled
slices of individual cells. Consistent with prior observations imaging
selected views in yeast {[}\protect\hyperlink{ref-T1Qr0xyP}{13}{]}, organelles
like the nucleus and mitochondria only showed sporadic targets detected
with low SNRs, consistent with the estimated false-positive rate of one
per tile. For each detected target we also calculated the Z positions
from the individual estimated defocus and defocus offset for each tile.
When viewed from the side, the ribosome positions therefore show the
slight tilts of the lamellae relative to the microscope frame of
reference (Fig. {[}\ref{fig:matching_euc}{]}B, Fig.
{[}\ref{fig:matching_fff}{]}B, 
Fig. {[}\ref{fig:matching_euc}{]}-video 1, Fig.
{[}\ref{fig:matching_fff}{]}-video 1). Furthermore, the side views indicated that lamellae were
thinner at the leading edge. To confirm this we estimated the ice
thickness in individual tiles using the Beer-Lambert law
{[}\protect\hyperlink{ref-17IP4Lhz1}{18}{]} with 322 nm as coefficient
{[}\protect\hyperlink{ref-17IP4Lhz1}{18}{]} (Fig.
{[}\ref{fig:lamella_motion_thickness}{]}B). We found that the thickness of the
lamellae varied between 100 and 250 nm, with consistently thinner ice at
the leading edge even though we prepared the lamellae with the
``overtilt'' approach {[}\protect\hyperlink{ref-hr3dyUeI}{19}{]}. To further confirm
the relationship of the range in Z-positions of detections and sample
thickness we plotted the range in Z-positions as a function of the
estimated sample thickness (Fig. {[}\ref{fig:lamella_motion_thickness}{]}C). For
most tiles, the apparent thickness of LSU detections was at least 70 nm
less than the estimated sample thickness, indicating that no detections
were being made within 35 nm of the lamella edge. It is possible that
this is caused by sample damage during FIB-milling as similar values for
damaged areas in FIB-milled lamellae have been estimated from
sub-tomogram averaging {[}\protect\hyperlink{ref-SDMGf7aG}{20}{]}. This means that
LSU detections across the lamellae can be skewed by a change in
thickness and sample damage. Therefore, better sample preparation
methods together with a better understanding of the damage to the sample
during FIB-milling are needed to accurately quantify molecular
concentrations.

@@

Close inspection of the LSU positions in the lamellae revealed several
interesting features. LSUs could be seen associating with membranes, in
patterns reminiscent of the rough endoplasmic reticulum (Fig.
{[}\ref{fig:matching_euc}{]}C, Fig. {[}\ref{fig:matching_fff}{]}C) or the outer nuclear
membrane (Fig. {[}\ref{fig:matching_euc}{]}D). We also observed LSUs forming
ring-like structures (Fig. {[}\ref{fig:matching_euc}{]}E), potentially indicating
circularized mRNAs {[}\protect\hyperlink{ref-cie13Q8F}{21}{]}. While ribosomes were for the most
part excluded from the numerous granules observed in the cytoplasm, in
some cases we observed clusters of LSUs in the inclusions of
double-membraned granules described earlier (Fig. {[}\ref{fig:matching_euc}{]}F,
Fig. {[}\ref{fig:matching_fff}{]}D,E). It is, in principle, possible that these
targets are situated above or below the imaged granules, since the
granule positions in z cannot be determined using 2D projections.
However, in the case of Fig. {[}\ref{fig:matching_fff}{]}E, the detected LSUs
span the whole lamella in the z direction (Fig. {[}\ref{fig:matching_fff}{]}F),
while positions above or below a granule would result in LSUs situated
exclusively at the top or bottom of the lamella. This is consistent with
the earlier hypothesis that the inclusions are of cytoplasmic origin.

@@

In this study we developed an approach to image entire cellular
cross-section using cryo-EM at high enough resolution to allow for 2DTM
detection of the LSU. The two main advantages compared to previous
approaches are high throughput of imaging and biological context for
detected molecules. The requirement to increase throughput in cryo-EM
data collection of cellular samples has been recognized in the recent
literature. Most approaches described so far are tailored towards
tomography. Peck et al. {[}\protect\hyperlink{ref-1GPPSX111}{22}{]} and Yang et al.
{[}\protect\hyperlink{ref-ujizcpVn}{23}{]} developed approaches to increase the
FOV of tomogram data-collection by using a montaging technique. Peck et
al.~used a similar ``condensed-beam'' approach as described here. However,
the montages are substantially smaller in scope, covering carbon film
holes of 2 µm diameter. Bouvette et al.
{[}\protect\hyperlink{ref-1Gwx5ScUa}{24}{]} and Eisenstein et al.
{[}\protect\hyperlink{ref-xvouNMBy}{25}{]} are using beam image-shift to collect
tilt-series in multiple locations in parallel to increase throughput.
However, none of these approaches provide the full coverage of a
cellular cross-section that can be achieved using DeCo-LACE.

We observed granules containing a vesicle of putative cytosolic origin.
We speculate that upon degranulation, the process in which granules fuse
with the plasma membrane, these vesicles would be released into the
extracelullar space. The main types of extracellular vesicles of this
size are exosomes, up to 100 nm large vesicles derived from fusion of
multivesicular bodies with the plasma membrane, and microvesicles, which
are derived from direct budding of the plasma membrane
{[}\protect\hyperlink{ref-kncnYGLD}{26}{]}. We suggest that granulocytes could release
a third type of extracellular vesicle, granule-derived vesicles (GDV),
into the extracellular space. 2DTM showed that a subset of GDVs can
contain ribosomes (Fig. {[}\ref{fig:matching_euc}{]}F, Fig.
{[}\ref{fig:matching_fff}{]}D,E). This could indicate that these vesicles are
transporting translation-capable mRNAs, as has been described for
exosomes {[}\protect\hyperlink{ref-agVdpX76}{27}{]}. Further studies will be necessary to
confirm the existence of GDVs in granulocytes isolated from mammals and
to understand their functional significance.

@@

We found that even though we used beam image-shift extensively (up to 7
um), we did not see substantially reduced 2DTM SNR values in tiles
acquired at high beam image-shift compared to tiles acquired with low or
no beam image-shift. This is unexpected because beam image-shift is
though to degrade the high-resolution signal due to the introduction of
beam-tilt, as has been observed in single particle analysis
{[}\protect\hyperlink{ref-44fG6kcy}{28},\protect\hyperlink{ref-wy8cRzrH}{29}{]}. The
signal detected by 2DTM is target and sample dependent and has been
shown to be sensitive to a resolution up to 3 Å, but in practice is
limited by the B-factor applied to the template
{[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]}. In our case, we used a structure of the
mouse LSU that was deposited into the PDB with atoms having a median
B-factor of \textasciitilde{} 80 Å\(^2\), which we multiplied by 1.5 before generating
the density map. This value was chosen empirically early in the study to
optimize the number of detections. The resulting median B-factor of 120
Å\(^2\) is equivalent to a Gaussian lowpass filter with a filter constant
of 7.7 Å. We did not measure the beam-tilt caused by beam-image shift on
the microscope to acquire our data, but Cheng et. al.~report that in
their measurements Krios Titan columns exhibited a beam-tilt of
0.17-0.25 mrad per μm of beam image-shift
{[}\protect\hyperlink{ref-wy8cRzrH}{29}{]}. We therefore expect a worst-case
beam-tilt of 1.75 mrad. At this beam-tilt we expect a phase error of
larger than π/4 at resolutions higher than 5.75 Å
{[}\protect\hyperlink{ref-wy8cRzrH}{29}{]}, which exceeds the resolution of our
2DTM template. We conclude that the beam-tilt caused by beam-image shift
did not strongly affect detections in the present study, but it might be
important to consider when imaging at even higher beam-image shift
values or when using higher resolution signal in 2DTM.

We used 2DTM of the ribosome LSU to verify the image quality of
DeCo-LACE data. However, 2DTM has the potential to detect many other
protein complexes. The model of the ribosomal LSU used in this
manuscript has a molecular weight of \textasciitilde2 MDa, \textasciitilde1.3 MDa of which is
nucleic acid. The higher scattering density of nucleic acid compared to
protein {[}\protect\hyperlink{ref-13fhsbtxo}{30}{]} may mean that a biomolecular complex of equal
size consisting of only protein would result in lower SNR values. Many
biological complexes are smaller and do not contain nucleic acid, but
simulations of 2DTM {[}\protect\hyperlink{ref-Ynb3IP6I}{7}{]} suggest that it should be
possible to detect protein molecules as small as 300 kDa in an crowded
environment. Besides the molecular weight we expect that the
conformational homogeneity of a protein complex will affect the ability
to detect it and note that for complexes that occur at low
concentrations inside the cell a higher detection threshold might be
necessary to reduce the number of false positives among the few true
targets that can be detected.

Since we observed substantial variation in LSU density within and
between lamellae, visual proteomics studies that use cryo-EM to
establish changes in molecular organization within cells will require
orders of magnitude more data than used in this study. One milestone
would be to image enough data to represent one cellular volume, which
for a small eukaryotic cells requires imaging approximately 100
lamellae. While data collection throughput on the TEM is fundamentally
limited by the exposure time, this amount of data could be collected
within 12 hours by improving the data acquisition scheme to perform all
necessary calculations in parallel with actual exposure of the camera.
Sample preparation using a FIB/SEM is also currently a bottleneck, but
preparation of large lamellae with multiple cellular cross-sections
using methods like WAFFLE {[}\protect\hyperlink{ref-17H2LWiIu}{31}{]} might allow
sufficient throughput. As stated in the results, at least for 2DTM
computation will remain challenging and approximately 17,000 GPU hours
would be required for a 100 lamellae dataset. It might be possible to
increase the performance of 2DTM by improving the implementation of
GPU-based fast Fourier transforms. Alternatively, strategies that
initially search images at lower resolution and sparser rotational
sampling, followed by refinement at higher resolution, could be more
efficient, but it is yet unclear whether this is feasible in cellular
samples with strong low-resolution background.

@@

\hypertarget{key-resources-table}{%
\subsubsection{Key Resources Table}\label{key-resources-table}}

\begin{tablenos:no-prefix-table-caption}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2139}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1148}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2451}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1148}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2951}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Reagent type
(species)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Designation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source or reference
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Identifiers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Additional Information
\end{minipage} \\
\midrule()
\endhead
cell line (\emph{mus
musculus}) & ER-HoxB8 & {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} & & Generated from mouse bone marrow as
described in
{[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} \\
peptide, recombinant protein & SCF & {[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} & & Generated from CHO-SCF cell line as
described in
{[}\protect\hyperlink{ref-1B9Vt9eYu}{10}{]} \\
chemical compound,
drug & Estrogen & Sigma & E8875 & \\
\bottomrule()
\end{longtable}

\end{tablenos:no-prefix-table-caption}

@@

ER-HoxB8 cells were generated as described by Wang et. al.
{[}\protect\hyperlink{ref-1B9Vt9eYu}{10},\protect\hyperlink{ref-nSMAxqTD}{32}{]}
and maintained in RPMI medium supplemented with 10\% FBS,
penicillin/streptomycin, SCF, and estrogen
 at 37 °C and 5\% CO2. 120 h prior to grid preparation, cells were washed twice in PBS and
cultured in the same medium except without estrogen. The authenticity of the
cells was verified by flow-cytometry and Giemsa staining after differentiation {[}\protect\hyperlink{ref-1B9Vt9eYu}{10},\protect\hyperlink{ref-nSMAxqTD}{32}{]}. Cells were then counted and diluted to \(1\cdot10^6\)
cells/ml. Grids (either 200 mesh copper grids, with a sillicone-oxide
and 2 µm holes with a 2 µm spacing or 200 mesh gold grids with a thin
gold film and 2 µm holes in 2 µm spacing) were glow-discharged from both
sides using a 15 mA for 45 s. 3.5 µl of cell suspension was added to
grids on the thin-film side and grids were blotted from the back side
using a GP2 cryoplunger (Leica, Wetzlar, Germany) for 8 s and rapidly
plunged into liquid ethane at -185 °C.

@@

A list of tile pairs \(i,j\) that overlap were assembled by selecting
images where \(|\mathbf{c}_i-\mathbf{c}_j| < D_{Beam}\). In order to
calculate the precise offset between tiles \(i\) and \(j\),
\(\mathbf{r}_{i,j}\), we calculated the cross-correlation between the two
tiles, masked to the overlapping illuminated area using the scikit-image
package {[}\protect\hyperlink{ref-stvWEJeu}{38}{]} was used to calculate refined offsets .
The coordinates \(\mathbf{c}_{i}\) were then refined by a least-square
minimization against \(\mathbf{r}_{i,j}\):

@@

\begin{fignos:tagged-figure}[1 - figure supplement 1]
